From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-09 Pi+/paper/discussion.tex
table

@@

% \begin{center}
%     \begin{tabular}{c c c}
%         \hline
%         $\PiLang$     & $\Sn$               & $\UFin$     \\
%         \hline
%         types         & Natural numbers     & Finite sets \\
%         \hline
%         1-combinators & Generators of $\Sn$ & 1-paths     \\
%         \hline
%         2-combinators & Relations of $\Sn$  & 2-paths     \\
%         \hline
%     \end{tabular}
% \end{center}

% \begin{center}
%     \begin{tabular}{c c c}
%         \hline
%         Logic                              & Program                       & Algebra                     \\
%         \hline
%         Propositions                       & Types                         & Objects                     \\
%         \hline
%         Proofs                             & Terms                         & Morphisms                   \\
%         \hline
%         $\blank$                           & Equations                     & Homotopies                  \\
%         \hline
%         Intuitionistic propositional logic & Simply typed Lambda Calculus  & Cartesian Closed Categories \\
%         \hline
%         Superstructural Reversible logic   & Reversible Language $\PiLang$ & Symmetric Rig Groupoids     \\
%         \hline
%         Connectives                        & Type constructors             & Bifunctors                  \\
%         \hline
%         ?                                  & Type normalisation            & ?                           \\
%         \hline
%         ?                                  & Program normalisation         & ?                           \\
%         \hline
%         ?                                  & Soundness of 2-combinators    & ?                           \\
%     \end{tabular}
% \end{center}

% \begin{center}
%     \begin{tabular}{c c c}
%         \hline
%         Reversible Logic             & Reversible Programming                  & Algebra                  \\
%         \hline
%         Free commutative rig         & Free symmetric rig groupoid             & $\UFin$                  \\
%         \hline
%         Propositions                 & Types                                   & Objects                  \\
%         \hline
%         Entailment?                  & Reversible programs                     & Isomorphisms             \\
%         \hline
%         $\blank$                     & 2-combinators                           & Homotopies               \\
%         \hline
%         Conjunction?                 & $\times$                                & $\otimes$                \\
%         \hline
%         Disjunction?                 & $+$                                     & $\oplus$                 \\
%         \hline
%         $A \land B \vdash B \land A$ & $\swapt$                                & $\mathcal{B}_{A,B}$      \\
%         \hline
%         True proposition             & $\onet$                                 & $F_1$                    \\
%         \hline
%         Decidability                 & Program Synthesis                       & Reachability in a graph? \\
%         \hline
%         Soundness/Completeness       & Soundness/Completeness of 1-combinators & ?                        \\
%     \end{tabular}
% \end{center}

>>>>

\begin{center}
    \begin{tabular}{c c c}
        \hline
        $\PiLang$     & $\Sn$               & $\UFin$     \\
        \hline
        types         & Natural numbers     & Finite sets \\
        \hline
        1-combinators & Generators of $\Sn$ & 1-paths     \\
        \hline
        2-combinators & Relations of $\Sn$  & 2-paths     \\
        \hline
    \end{tabular}
\end{center}

\begin{center}
    \begin{tabular}{c c c}
        \hline
        Logic                              & Program                       & Algebra                     \\
        \hline
        Propositions                       & Types                         & Objects                     \\
        \hline
        Proofs                             & Terms                         & Morphisms                   \\
        \hline
        $\blank$                           & Equations                     & Homotopies                  \\
        \hline
        Intuitionistic propositional logic & Simply typed Lambda Calculus  & Cartesian Closed Categories \\
        \hline
        Superstructural Reversible logic   & Reversible Language $\PiLang$ & Symmetric Rig Groupoids     \\
        \hline
        Connectives                        & Type constructors             & Bifunctors                  \\
        \hline
        ?                                  & Type normalisation            & ?                           \\
        \hline
        ?                                  & Program normalisation         & ?                           \\
        \hline
        ?                                  & Soundness of 2-combinators    & ?                           \\
    \end{tabular}
\end{center}

\begin{center}
    \begin{tabular}{c c c}
        \hline
        Reversible Logic             & Reversible Programming                  & Algebra                  \\
        \hline
        Free commutative rig         & Free symmetric rig groupoid             & $\UFin$                  \\
        \hline
        Propositions                 & Types                                   & Objects                  \\
        \hline
        Entailment?                  & Reversible programs                     & Isomorphisms             \\
        \hline
        $\blank$                     & 2-combinators                           & Homotopies               \\
        \hline
        Conjunction?                 & $\times$                                & $\otimes$                \\
        \hline
        Disjunction?                 & $+$                                     & $\oplus$                 \\
        \hline
        $A \land B \vdash B \land A$ & $\swapt$                                & $\mathcal{B}_{A,B}$      \\
        \hline
        True proposition             & $\onet$                                 & $F_1$                    \\
        \hline
        Decidability                 & Program Synthesis                       & Reachability in a graph? \\
        \hline
        Soundness/Completeness       & Soundness/Completeness of 1-combinators & ?                        \\
    \end{tabular}
\end{center}

@@
